### 2013-07-02 PaperDraft.Rmd
paper: initial introduction text, 2

Os polinómios proporcionam um dos casos mais simples de modelos não-lineares. Além disso as funções polinomiais constituem uma das áreas mais aprofundadas da matemática. Esta característica de limiar torna o estudo dos modelos polinomiais especialmente atractiva.
-->
With notable exceptions, most machine learning techniques are based on linear models. This assumption has many advantages in its favor spanning, for example, reduced computational complexity and strong theoretical framework. Though sometimes linear models are adequate, many nonlinear problems without acceptable linear approximations are left, as can be seen by the number of articles that describe applications of nonlinear models in engineering, economics, linguistics, animal production, _etc_.

@@

>>>>

Os polinómios proporcionam um dos casos mais simples de modelos não-lineares. Além disso as funções polinomiais constituem uma das áreas mais aprofundadas da matemática. Esta característica de limiar torna o estudo dos modelos polinomiais especialmente atractiva.
-->
With notable exceptions, most machine learning techniques are based on linear models. This assumption has many advantages spanning, for example, reduced computational complexity and strong theoretical framework. Though sometimes linear models are adequate, many nonlinear problems without acceptable linear approximations are left, as can be seen by the number of articles that describe applications of nonlinear models in engineering, economics, linguistics, animal production, _etc_.

@@

In this setting, the use of genetic algorithms to search for optimal parameters of polynomial models is unavoidable. Indeed, many applied works can be found under this keywords, with special incidence on engineering and biology, where often the required models do not admit acceptable linear approximations.

The specific nature of polynomials allows quite different representations of individual instances. For example, $$$p(x) = x^2 - 1 = (x-1)(x+1)$$$ can be described either by:

* a list of coefficients: `[-1, 0, 1]`;
* the product of two lower degree polynomials;
* a parse tree: `sum(square(x),-1)`;
